Semilattice Graphs for Distributed Databases

### 2022-10-04 paper/paper.tex
fix typo
serialize and enum lat graphs

      It is somewhat unwieldy to define $l_k$ and $t_k$ in implementation, since they depend on a possibly-infinite mapping. Accordingly, we define a notion of \emph{dependencies} of a function. For a key $k : K$ sets $X, Y$, a function $f : X \times (K_{<k} \rightarrow V) \rightarrow S$ has dependencies according to a function $d : X \rightarrow 2^{K_{<k}}$ when for any $x : X, m, m' : K_{<k} \rightarrow V$, if $m(k') = m'(k')$ for each $k' : d(x)$, we have $f(x, m) = f(x, m')$.

      Now we apply this to $l_k, t_k$. Let $d_k^\star : 2^{K_{<k}}$ be a set of lattice dependencies, and $d_{k}(v) : 2^{K_{<k}}$ be a set of value dependencies for $v \in V$. We say $(l_k, d_k)$ have dependencies according to $d_{k, l}, d_{k, v}$ if:

      \begin{itemize}
        \item $\mathrm{Elems}(l_k(m))$ only depends on $m(k')$ for each $k' \in d_^\star$.
        \item $\bot_{l_k(m})$ only depends on $m(k')$ for each $k' \in d_k^\star$.
        \item $t_k(m, m')(v)$ only depends on $m(k')$ and $m'(k')$ for each $k' \in d_k^\star \cup d_k(v)$.
        \item $x \vee_{l_k(m)} y$ only depends on $m(k')$ for each $k' \in d_k^\star \cup d_k(x) \cup d_k(y)$.
      \end{itemize}

>>>>

      It is somewhat unwieldy to define $l_k$ and $t_k$ in implementation, since they depend on a possibly-infinite mapping. Accordingly, we assume that these operations only depend on a defined set of values. Let $d_k^\star : 2^{K_{<k}}$ be a set of lattice dependencies, and $d_{k}(v) : 2^{K_{<k}}$ be a set of value dependencies for $v \in V$. Both dependency sets must only include keys less than $k$. We say $(l_k, d_k)$ have dependencies according to $d_{k, l}, d_{k, v}$ if:

      \begin{itemize}
        \item $\mathrm{Elems}(l_k(m))$ only depends on $m(k')$ for each $k' \in d_k^\star$.
        \item $\bot_{l_k(m})$ only depends on $m(k')$ for each $k' \in d_k^\star$.
        \item $t_k(m, m')(v)$ only depends on $m(k')$ and $m'(k')$ for each $k' \in d_k^\star \cup d_k(v)$.
        \item $x \vee_{l_k(m)} y$ only depends on $m(k')$ for each $k' \in d_k^\star \cup d_k(x) \cup d_k(y)$.
      \end{itemize}

      To ensure dependency sets don't grow unexpectedly, we require:
      \begin{itemize}
        \item $d_k(t_k(m, m')(v)) \subseteq d_k(v)$.
        \item $d_k(x \vee_{l_k(m)} y) \subseteq d_k(x) \cup d_k(y)$.
      \end{itemize}
